---
title: "Bulk RNA-seq report"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: hide
    self_contained: true
params:
  counts: "../results/featurecounts/counts.tsv"
  samplesheet: "../results/pipeline_info/samplesheet.csv"
  gene_names: "../results/featurecounts/gene_names.tsv"
  qc_summary: "../results/qc/qc_summary.tsv"
  strand_report: "../results/star/strandedness_mqc.tsv"
  versions: "../results/pipeline_info/versions.tsv"
  multiqc_link: "../results/multiqc/multiqc_report.html"
  design: "~ condition"
  contrasts: ""
  padj_cutoff: 0.05
  lfc_cutoff: 0.58
  genome: "GRCh38"
  ensembl_release: "112"
  strandedness: "auto"
  skip_enrichment: false
  tables_dir: "tables"
---

```{r setup, include = FALSE}
# HOW TO RUN THIS REPORT WITHOUT NEXTFLOW
#   1. Open this file in RStudio (or use the Docker image, see docs/usage.md).
#   2. Check the paths under `params:` above point at your pipeline results folder.
#      The defaults work when results/ sits next to the report/ folder.
#   3. Change what you need (contrasts, cutoffs, design) and click "Knit".
#   From R instead:
#     rmarkdown::render("rnaseq_report.Rmd", params = list(contrasts = "treated_vs_control"))
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5)
suppressPackageStartupMessages({
  library(DESeq2)
  library(edgeR)
  library(limma)
  library(ggplot2)
  library(pheatmap)
  library(DT)
})
theme_set(theme_bw())

# Thresholds used for QC flags and GO. Change them here if your data need it.
MIN_PCT_UNIQUE   <- 60  # % uniquely mapped reads below this is flagged
MIN_PCT_ASSIGNED <- 50  # % reads assigned to genes below this is flagged
MIN_GO_GENES     <- 5   # fewer significant genes than this: skip GO for that list
REPORT_DIR <- dirname(knitr::current_input(dir = TRUE))
```

This report was made by **bulk-rnaseq-lite-nf**. Click a **Code** button to see the R code behind any result.

# Warnings and checks

```{r load-data}
# Read the count matrix: one row per gene, one column per sample.
counts_df <- read.delim(params$counts, check.names = FALSE)
counts <- as.matrix(counts_df[, -1, drop = FALSE])
rownames(counts) <- counts_df$gene_id

# Read the samplesheet and put its rows in the same order as the count columns.
# Everything is read as text first, so IDs like "01" or a condition called "T" stay as written.
samples <- read.csv(params$samplesheet, colClasses = "character", check.names = FALSE,
                    fileEncoding = "UTF-8-BOM", strip.white = TRUE)
missing_samples <- setdiff(colnames(counts), samples$sample)
if (length(missing_samples) > 0) {
  stop("These count columns are not in the samplesheet: ", paste(missing_samples, collapse = ", "))
}
# Condition levels keep the samplesheet order; the first one is the reference.
condition_levels <- unique(samples$condition)
samples <- samples[match(colnames(counts), samples$sample), , drop = FALSE]
rownames(samples) <- samples$sample
samples$condition <- factor(samples$condition,
                            levels = condition_levels[condition_levels %in% samples$condition])

# Gene symbols (from the GTF), QC numbers and tool versions written by the pipeline.
gene_names <- read.delim(params$gene_names)
symbol_of <- setNames(gene_names$gene_name, gene_names$gene_id)
qc <- read.delim(params$qc_summary, check.names = FALSE, na.strings = "NA")
versions <- if (file.exists(params$versions)) {
  read.delim(params$versions, header = FALSE, col.names = c("tool", "version"))
}
strand_tab <- if (file.exists(params$strand_report) && basename(params$strand_report) != "NO_FILE") {
  read.delim(params$strand_report, comment.char = "#")
}
strand_used <- if (!is.null(strand_tab)) {
  paste(unique(strand_tab$call), "(auto-detected)")
} else {
  paste(params$strandedness, "(set by user)")
}
```

```{r checks}
report_warnings <- character()

# Condition names must be valid R names so DESeq2/edgeR can name coefficients.
lv <- levels(samples$condition)
if (any(make.names(lv) != lv)) {
  stop("Condition values must start with a letter and use only letters, digits, '.' or '_': ",
       paste(lv, collapse = ", "))
}

# Turn the design text (e.g. "~ batch + condition") into a list of columns.
design_vars <- trimws(strsplit(sub("^\\s*~", "", params$design), "+", fixed = TRUE)[[1]])
design_vars <- design_vars[nzchar(design_vars)]
if (length(design_vars) == 0 || tail(design_vars, 1) != "condition") {
  stop("The design must end with 'condition', e.g. '~ batch + condition'.")
}
not_found <- setdiff(design_vars, colnames(samples))
if (length(not_found) > 0) {
  stop("Design columns missing from the samplesheet: ", paste(not_found, collapse = ", "))
}
# Covariates: text (like batch "A"/"B") becomes a factor; real numbers (like RIN) stay numeric.
# A column of a few whole numbers (batch coded 1/2/3) is almost always labels, so it becomes a factor.
for (v in setdiff(design_vars, "condition")) {
  num <- suppressWarnings(as.numeric(samples[[v]]))
  if (anyNA(num)) {
    samples[[v]] <- factor(samples[[v]])
  } else if (all(num == round(num)) && length(unique(num)) <= 5) {
    samples[[v]] <- factor(samples[[v]])
    report_warnings <- c(report_warnings, sprintf(
      "Column '%s' has only %d whole-number values (%s), so it was treated as labels (like batches), not as a continuous number. Use text labels (e.g. b1, b2) to avoid this note.",
      v, length(unique(num)), paste(sort(unique(num)), collapse = ", ")))
  } else {
    samples[[v]] <- num
  }
}

# Check 1: can the design be estimated? A batch that lines up exactly with condition
# cannot be separated from it, so we fall back to '~ condition'.
mm <- model.matrix(as.formula(paste("~", paste(design_vars, collapse = " + "))), samples)
if (qr(mm)$rank < ncol(mm)) {
  report_warnings <- c(report_warnings, sprintf(
    "The design '%s' cannot be estimated (a covariate is confounded with condition). It was replaced by '~ condition'.",
    params$design))
  design_vars <- "condition"
  mm <- model.matrix(~ condition, samples)
}
design_formula <- as.formula(paste("~", paste(design_vars, collapse = " + ")))

# Check 2: replicates per group.
reps <- table(samples$condition)
if (any(reps < 2)) {
  report_warnings <- c(report_warnings, sprintf(
    "Groups with fewer than 2 replicates: %s. Their results are unreliable.",
    paste(names(reps)[reps < 2], collapse = ", ")))
}

# Check 3: testing needs more samples than model coefficients.
can_test <- nrow(mm) > ncol(mm)
if (!can_test) {
  report_warnings <- c(report_warnings,
    "Not enough samples to estimate variability (no residual degrees of freedom). Differential expression was skipped.")
}

# Check 4: low assignment usually means wrong strandedness or annotation.
low_assigned <- qc$sample[!is.na(qc$pct_assigned) & qc$pct_assigned < MIN_PCT_ASSIGNED]
if (length(low_assigned) > 0) {
  report_warnings <- c(report_warnings, sprintf(
    "Less than %d%% of reads were assigned to genes in: %s. Check strandedness and annotation.",
    MIN_PCT_ASSIGNED, paste(low_assigned, collapse = ", ")))
}

# Remove genes with too few counts to test. filterByExpr keeps genes with enough
# counts in at least as many samples as the smallest group.
y_all <- DGEList(counts)
keep <- filterByExpr(y_all, group = samples$condition)
counts_f <- counts[keep, , drop = FALSE]
if (sum(keep) < 2) {
  can_test <- FALSE
  report_warnings <- c(report_warnings, "Fewer than 2 genes passed filtering. Differential expression was skipped.")
}

# Contrasts: "A_vs_B" compares A with B (positive log2FC = higher in A).
# Empty = every condition against the first (reference) condition.
contrast_list <- if (is.null(params$contrasts) || !nzchar(params$contrasts)) {
  lapply(lv[-1], function(l) c(l, lv[1]))
} else {
  lapply(trimws(strsplit(params$contrasts, ",")[[1]]), function(x) {
    ab <- strsplit(x, "_vs_", fixed = TRUE)[[1]]
    if (length(ab) != 2 || !all(ab %in% lv)) {
      stop(sprintf("Contrast '%s' is not valid. Write LEVEL_vs_LEVEL using: %s", x, paste(lv, collapse = ", ")))
    }
    ab
  })
}
names(contrast_list) <- vapply(contrast_list, paste, character(1), collapse = "_vs_")
```

```{r show-warnings, echo = FALSE, results = "asis"}
if (length(report_warnings) > 0) {
  cat(paste0("> **Warning:** ", report_warnings, collapse = "\n>\n"), "\n")
} else {
  cat("All checks passed.\n")
}
```

# 1. Run summary

```{r run-summary}
# The settings this report was made with.
run_info <- data.frame(
  setting = c("Genome", "Ensembl release", "Strandedness", "Design (used)", "Contrasts",
              "padj cutoff", "|log2FC| cutoff", "GO enrichment"),
  value = c(params$genome, as.character(params$ensembl_release), strand_used,
            paste(deparse(design_formula), collapse = ""), paste(names(contrast_list), collapse = ", "),
            params$padj_cutoff, params$lfc_cutoff,
            if (isTRUE(params$skip_enrichment)) "skipped" else "GO BP/MF/CC (DESeq2 significant genes)"))
knitr::kable(run_info)
```

```{r versions}
# Tool versions (container images) used by the pipeline.
if (!is.null(versions)) knitr::kable(versions)
```

```{r sample-table}
# The samples and their design columns.
knitr::kable(samples[, setdiff(colnames(samples), c("fastq_1", "fastq_2")), drop = FALSE], row.names = FALSE)
```

# 2. Upstream QC

Detailed per-tool plots are in the [MultiQC report](`r params$multiqc_link`).

```{r qc-table}
# One row per sample. Flagged: uniquely mapped < MIN_PCT_UNIQUE % or assigned < MIN_PCT_ASSIGNED %.
qc$flag <- ifelse((!is.na(qc$pct_uniquely_mapped) & qc$pct_uniquely_mapped < MIN_PCT_UNIQUE) |
                  (!is.na(qc$pct_assigned) & qc$pct_assigned < MIN_PCT_ASSIGNED), "CHECK", "")
knitr::kable(qc, digits = 1, row.names = FALSE)
```

```{r qc-plot, fig.height = 0.4 * nrow(qc) + 2}
# Mapping and gene-assignment rates. Dashed lines are the flag thresholds.
qc_long <- rbind(
  data.frame(sample = qc$sample, metric = "% uniquely mapped", value = qc$pct_uniquely_mapped),
  data.frame(sample = qc$sample, metric = "% assigned to genes", value = qc$pct_assigned))
ggplot(qc_long, aes(sample, value, fill = metric)) +
  geom_col(position = "dodge") +
  geom_hline(yintercept = c(MIN_PCT_UNIQUE, MIN_PCT_ASSIGNED), linetype = "dashed") +
  coord_flip() + labs(x = NULL, y = "%", fill = NULL)
```

```{r strand-table}
# Strandedness per sample (auto mode only): forward fraction ~0.5 unstranded, high forward, low reverse.
if (!is.null(strand_tab)) knitr::kable(strand_tab, row.names = FALSE)
```

# 3. Count QC

```{r library-sizes, fig.height = 0.4 * ncol(counts) + 2}
# Library size (reads counted on genes) and number of genes with at least one read.
lib <- data.frame(sample = colnames(counts), million_reads = colSums(counts) / 1e6,
                  genes_detected = colSums(counts > 0), condition = samples$condition)
ggplot(lib, aes(sample, million_reads, fill = condition)) + geom_col() + coord_flip() +
  labs(x = NULL, y = "Million reads assigned to genes")
ggplot(lib, aes(sample, genes_detected, fill = condition)) + geom_col() + coord_flip() +
  labs(x = NULL, y = "Genes with at least one read")
```

```{r logcpm-distribution}
# Distribution of log2 counts-per-million per sample. Boxes should look similar.
logcpm <- cpm(y_all, log = TRUE)
ggplot(data.frame(sample = rep(colnames(logcpm), each = nrow(logcpm)), value = as.vector(logcpm)),
       aes(sample, value)) +
  geom_boxplot(outlier.size = 0.3) + coord_flip() + labs(x = NULL, y = "log2 CPM")
```

**Gene filtering:** `r sum(keep)` of `r length(keep)` genes had enough counts to be tested (`edgeR::filterByExpr`).

# 4. Sample relationships

```{r transform}
# Variance-stabilising transformation (VST) makes counts comparable across genes for
# PCA and heatmaps. vst() needs >= 1000 genes; smaller data use the slower full version,
# and if that fails we fall back to log2(normalised counts + 1).
dds <- DESeqDataSetFromMatrix(counts_f, samples, design_formula)
dds <- estimateSizeFactors(dds)
transform_used <- "VST"
vsd_mat <- tryCatch(
  assay(if (nrow(dds) >= 1000) vst(dds, blind = TRUE) else varianceStabilizingTransformation(dds, blind = TRUE)),
  error = function(e) {
    transform_used <<- "log2(normalised counts + 1)"
    log2(counts(dds, normalized = TRUE) + 1)
  })
```

Transformation used for this section: **`r transform_used`**.

```{r pca-function}
# PCA on the 500 most variable genes. Colour = condition, shape = first covariate (e.g. batch).
covariates <- setdiff(design_vars, "condition")
plot_pca <- function(mat, title) {
  top <- head(order(apply(mat, 1, var), decreasing = TRUE), min(500, nrow(mat)))
  pca <- prcomp(t(mat[top, , drop = FALSE]))
  var_pct <- 100 * pca$sdev^2 / sum(pca$sdev^2)
  df <- cbind(as.data.frame(pca$x[, 1:2]), samples)
  p <- ggplot(df, aes(PC1, PC2, colour = condition, label = sample)) +
    geom_point(size = 3) +
    geom_text(vjust = -1, size = 3, show.legend = FALSE) +
    labs(title = title, x = sprintf("PC1 (%.1f%%)", var_pct[1]), y = sprintf("PC2 (%.1f%%)", var_pct[2]))
  if (length(covariates) > 0 && is.factor(df[[covariates[1]]])) p <- p + aes(shape = .data[[covariates[1]]])
  list(plot = p, var_pct = var_pct)
}
pca_raw <- plot_pca(vsd_mat, "PCA")
pca_raw$plot
```

```{r scree, fig.height = 3}
# How much variation each principal component explains.
n_pc <- min(4, length(pca_raw$var_pct))
ggplot(data.frame(PC = paste0("PC", seq_len(n_pc)), pct = pca_raw$var_pct[seq_len(n_pc)]), aes(PC, pct)) +
  geom_col() + labs(x = NULL, y = "% variance explained")
```

```{r distance-heatmap, fig.height = 5}
# Euclidean distances between samples: replicates should cluster together.
pheatmap(as.matrix(dist(t(vsd_mat))), annotation_col = samples[, design_vars, drop = FALSE],
         main = "Sample-to-sample distances")
```

```{r batch-corrected-pca}
# If the design has covariates, show the PCA after removing them (for display only;
# DE uses the covariates in the model instead of corrected values).
if (length(covariates) > 0) {
  factor_covs <- covariates[vapply(covariates, function(v) is.factor(samples[[v]]), logical(1))]
  numeric_covs <- setdiff(covariates, factor_covs)
  corrected <- removeBatchEffect(
    vsd_mat,
    batch = if (length(factor_covs) >= 1) samples[[factor_covs[1]]],
    batch2 = if (length(factor_covs) >= 2) samples[[factor_covs[2]]],
    covariates = if (length(numeric_covs) > 0) as.matrix(samples[, numeric_covs, drop = FALSE]),
    design = model.matrix(~ condition, samples))
  plot_pca(corrected, paste("PCA after removing", paste(covariates, collapse = " + ")))$plot
}
```

# 5. Differential expression {.tabset}

```{r differential-expression}
# DESeq2 (Wald test, apeglm-shrunk fold changes) and edgeR (quasi-likelihood F-test)
# run on the same filtered counts. A gene is significant when
# padj < padj_cutoff and |log2FC| > lfc_cutoff (unshrunk log2FC, for both methods).
is_significant <- function(x) !is.na(x$padj) & x$padj < params$padj_cutoff & abs(x$log2FC) > params$lfc_cutoff
de <- list()
if (can_test) {
  dds <- DESeq(dds, quiet = TRUE)
  # edgeR: one column per condition (~ 0 + condition + covariates), so contrasts are differences of columns.
  mm_edger <- model.matrix(as.formula(paste(c("~ 0 + condition", covariates), collapse = " + ")), samples)
  y <- estimateDisp(calcNormFactors(DGEList(counts_f)), mm_edger)
  fit <- glmQLFit(y, mm_edger)

  for (cn in names(contrast_list)) {
    a <- contrast_list[[cn]][1]
    b <- contrast_list[[cn]][2]
    # DESeq2: make B the reference level so the coefficient is exactly "condition_A_vs_B".
    dds_b <- dds
    dds_b$condition <- relevel(dds_b$condition, ref = b)
    dds_b <- nbinomWaldTest(dds_b, quiet = TRUE)
    coef <- paste0("condition_", a, "_vs_", b)
    res <- results(dds_b, name = coef, alpha = params$padj_cutoff)
    shrunk <- lfcShrink(dds_b, coef = coef, res = res, type = "apeglm", quiet = TRUE)
    d <- data.frame(gene_id = rownames(res), gene_name = unname(symbol_of[rownames(res)]),
                    baseMean = res$baseMean, log2FC = res$log2FoldChange,
                    log2FC_shrunk = shrunk$log2FoldChange, pvalue = res$pvalue, padj = res$padj)
    # edgeR
    con <- makeContrasts(contrasts = sprintf("condition%s - condition%s", a, b), levels = mm_edger)
    tt <- topTags(glmQLFTest(fit, contrast = con), n = Inf, sort.by = "none")$table
    e <- data.frame(gene_id = rownames(tt), gene_name = unname(symbol_of[rownames(tt)]),
                    logCPM = tt$logCPM, log2FC = tt$logFC, pvalue = tt$PValue, padj = tt$FDR)
    d$significant <- is_significant(d)
    e$significant <- is_significant(e)
    de[[cn]] <- list(deseq2 = d[order(d$padj), ], edger = e[order(e$padj), ])
  }
}

# Save full result tables (one CSV per contrast and method).
dir.create(params$tables_dir, showWarnings = FALSE, recursive = TRUE)
for (cn in names(de)) {
  write.csv(de[[cn]]$deseq2, file.path(params$tables_dir, paste0(cn, "_deseq2.csv")), row.names = FALSE)
  write.csv(de[[cn]]$edger, file.path(params$tables_dir, paste0(cn, "_edger.csv")), row.names = FALSE)
}
```

```{r contrast-tabs, echo = FALSE, results = "asis"}
# One tab per contrast, built from the template in _contrast.Rmd.
if (can_test) {
  for (cn in names(de)) {
    cat(knitr::knit_child(file.path(REPORT_DIR, "_contrast.Rmd"), envir = environment(), quiet = TRUE), sep = "\n")
  }
} else {
  cat("Differential expression was skipped (see Warnings).\n")
}
```

# 6. DESeq2 vs edgeR

```{r concordance}
# How well the two methods agree: overlap of significant genes and fold-change correlation.
if (can_test) {
  conc <- do.call(rbind, lapply(names(de), function(cn) {
    m <- merge(de[[cn]]$deseq2[, c("gene_id", "log2FC", "significant")],
               de[[cn]]$edger[, c("gene_id", "log2FC", "significant")],
               by = "gene_id", suffixes = c("_deseq2", "_edger"))
    m$contrast <- cn
    m$category <- ifelse(m$significant_deseq2 & m$significant_edger, "both",
                  ifelse(m$significant_deseq2, "DESeq2 only",
                  ifelse(m$significant_edger, "edgeR only", "neither")))
    m
  }))
  concordance <- do.call(rbind, lapply(split(conc, conc$contrast), function(m) data.frame(
    contrast = m$contrast[1],
    both = sum(m$category == "both"),
    deseq2_only = sum(m$category == "DESeq2 only"),
    edger_only = sum(m$category == "edgeR only"),
    spearman_log2FC = round(cor(m$log2FC_deseq2, m$log2FC_edger, method = "spearman", use = "complete.obs"), 3))))
  knitr::kable(concordance, row.names = FALSE)
}
```

```{r concordance-plot, fig.width = 8}
# Each point is a gene: DESeq2 fold change (x) against edgeR fold change (y).
if (can_test) {
  ggplot(conc, aes(log2FC_deseq2, log2FC_edger, colour = category)) +
    geom_point(size = 0.8, alpha = 0.7) +
    geom_abline(linetype = "dashed") +
    scale_colour_manual(values = c(both = "firebrick", `DESeq2 only` = "darkorange",
                                   `edgeR only` = "steelblue", neither = "grey70")) +
    facet_wrap(~ contrast) +
    labs(x = "DESeq2 log2FC", y = "edgeR log2FC", colour = NULL)
}
```

# 7. GO enrichment

```{r go-enrichment, results = "asis", fig.width = 9, fig.height = 9}
# Over-representation of GO terms (BP, MF, CC) among DESeq2 significant genes,
# up- and down-regulated separately. Background = all genes that passed filtering.
# GENCODE IDs carry a version (ENSG00000141510.18); the GO databases use the bare ID.
orgdb <- switch(params$genome, GRCh38 = "org.Hs.eg.db", GRCm39 = "org.Mm.eg.db", NULL)
go_enabled <- can_test && !isTRUE(params$skip_enrichment) && !is.null(orgdb)
strip_version <- function(ids) sub("\\.[0-9]+$", "", ids)
universe_ids <- strip_version(rownames(counts_f))
ids_match <- TRUE
if (go_enabled) {
  # If almost no gene IDs are known to the database, --genome probably doesn't match the reference.
  known <- AnnotationDbi::keys(getExportedValue(orgdb, orgdb), keytype = "ENSEMBL")
  n_found <- sum(universe_ids %in% known)
  cat(sprintf("%d of %d tested genes were found in %s.\n\n", n_found, length(universe_ids), orgdb))
  ids_match <- n_found >= 0.1 * length(universe_ids)
}
run_go <- function(genes) {
  if (length(genes) < MIN_GO_GENES) return(NULL)
  ego <- tryCatch(
    clusterProfiler::enrichGO(strip_version(genes), OrgDb = orgdb, keyType = "ENSEMBL", ont = "ALL",
                              universe = universe_ids, pvalueCutoff = 0.05, readable = TRUE),
    error = function(e) NULL)
  if (is.null(ego) || nrow(as.data.frame(ego)) == 0) NULL else ego
}
if (go_enabled && !ids_match) {
  cat(sprintf("**Gene IDs do not match %s**, so GO enrichment was skipped. Check that --genome matches your reference (GRCh38 = human, GRCm39 = mouse).\n", orgdb))
} else if (!go_enabled) {
  cat(if (isTRUE(params$skip_enrichment)) "GO enrichment was skipped (--skip_enrichment).\n"
      else if (is.null(orgdb)) "GO enrichment is only available for GRCh38 and GRCm39.\n"
      else "Differential expression was skipped, so there is nothing to test.\n")
} else {
  for (cn in names(de)) {
    d <- de[[cn]]$deseq2
    for (direction in c("up", "down")) {
      genes <- d$gene_id[d$significant & (if (direction == "up") d$log2FC > 0 else d$log2FC < 0)]
      ego <- run_go(genes)
      cat("\n\n## ", cn, ": ", direction, "-regulated (", length(genes), " genes)\n\n", sep = "")
      if (is.null(ego)) {
        cat("No enriched GO terms (or fewer than ", MIN_GO_GENES, " significant genes).\n\n", sep = "")
      } else {
        write.csv(as.data.frame(ego), file.path(params$tables_dir, paste0(cn, "_go_", direction, ".csv")), row.names = FALSE)
        print(enrichplot::dotplot(ego, showCategory = 10, split = "ONTOLOGY", label_format = 60) +
                facet_grid(ONTOLOGY ~ ., scales = "free_y") + ggtitle(paste(cn, direction)))
        cat("\n\n")
      }
    }
  }
}
```

# 8. Exported files

```{r exports, results = "asis"}
# Every CSV written by this report (in the tables/ folder next to the report).
files <- list.files(params$tables_dir)
cat(if (length(files) > 0) paste0("- `tables/", files, "`", collapse = "\n") else "No tables were written.", "\n")
```

## R session

```{r session-info}
# Package versions, for reproducibility.
sessionInfo()
```
